Additional analysis

### 2018-04-20 03_additional-analysis.Rmd
Show voluntarism and religiosity

newdata_conditions_c <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
  mutate(id = 1) %>% 
  left_join(select(newdata_means, -give_charity_3), by = "id") %>% 
  select(-id)

chains_fitted_c <- posterior_linpred(m_amount_c_full, 
                                     newdata = newdata_conditions_c)

coef_summary_c <- newdata_conditions_c %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_c), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))

ggplot(coef_summary_c, aes(x = fct_rev(give_charity_3), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "How often do you give to charity?", y = "Median amount donated") +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

>>>>

newdata_conditions_charity <- results %>% expand(nesting(crackdown, give_charity_3)) %>% 
  mutate(id = 1) %>% 
  left_join(select(newdata_means, -give_charity_3), by = "id") %>% 
  select(-id)

chains_fitted_charity <- posterior_linpred(m_amount_c_full, 
                                           newdata = newdata_conditions_charity)

coef_summary_charity <- newdata_conditions_charity %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_charity), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, give_charity_3), funs(fct_inorder(., ordered = TRUE)))

ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "How often do you give to charity?", y = "Median amount donated") +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

**Voluntarism and religiosity**

```{r plot-vol-relig-amounts}
newdata_conditions_vol_relig <- results %>% 
  expand(nesting(crackdown, volunteer, religiosity_bin)) %>% 
  filter(!is.na(religiosity_bin)) %>% 
  mutate(id = 1) %>% 
  left_join(select(newdata_means, -volunteer, -religiosity_bin), by = "id") %>% 
  select(-id)

chains_fitted_vol_relig <- posterior_linpred(m_amount_c_full, 
                                             newdata = newdata_conditions_vol_relig)

coef_summary_vol_relig <- newdata_conditions_vol_relig %>% 
  bind_cols(tidyMCMC(as.mcmc(chains_fitted_vol_relig), estimate.method = "median",
                     conf.int = TRUE, conf.level = 0.9, conf.method = "HPDinterval")) %>% 
  mutate_at(vars(crackdown, volunteer, religiosity_bin), funs(fct_inorder(., ordered = TRUE))) %>% 
  mutate(religiosity_bin = fct_recode(religiosity_bin,
                                      `Rarely attend religious services` = "Rarely",
                                      `Attend religious services\nat least once a month` = 
                                        "At least once a month"))

ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
  facet_wrap(~ religiosity_bin) +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```
